Detecting Treatment-Subgroup Interactions in Clustered Data with Generalized Linear Mixed-Effects Model Trees

### 2015-09-21 pkg/glmertree/paper/report.Rnw
added title for EW in acknowledgements
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@798 255f4249-2263-4417-b1ea-8498779e27a7

The authors would like to thank Prof.~Pim Cuijpers, Prof.~Jeanne Miranda, Dr.~Boadie Dunlop, Prof.~Rob DeRubeis, Prof.~Zindel Segal, Dr.~Sona Dimidjian, Prof.~Steve Hollon and Erica Weitz for granting access to the dataset for the application. The work for this paper was partially done while MF, AZ and TH were visiting the Institute for Mathematical Sciences, National University of Singapore in 2014. The visit was supported by the Institute.

>>>>

The authors would like to thank Prof.~Pim Cuijpers, Prof.~Jeanne Miranda, Dr.~Boadie Dunlop, Prof.~Rob DeRubeis, Prof.~Zindel Segal, Dr.~Sona Dimidjian, Prof.~Steve Hollon and Erica Weitz,~MA, for granting access to the dataset for the application. The work for this paper was partially done while MF, AZ and TH were visiting the Institute for Mathematical Sciences, National University of Singapore in 2014. The visit was supported by the Institute.
